Asymptotic-Preserving Discretization of Three-Dimensional Plasma Fluid Models

### 2023-10-17 paper_version/main.tex
minor change

We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma
model which boils down to an extended Euler-Maxwell system. Our method is inspired by and
extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief,
\emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of
Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. It can cope with large variations
of the so-called Debye length $\lambda_D$ and is robust in the quasi-neutral
singular-perturbation limit $\lambda_D\to 0$, because it enjoys an
\emph{asymptotic-preserving} (AP) property in the sense that in the sense that the limit
$\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit
model. The key ingredients of our approach are (i) a discretization of Maxwell's equations
based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC)
also known the finite integration technique (FIT), (ii) a finite volume method (FVM) for
the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping},
(iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v)
additional \emph{stabilization} in the non-conducting region outside the plasma domain
based on direct enforcement of Gauss' law. Numerical tests provide strong evidence
confirming the AP property of the new method.

>>>>

We elaborate a numerical method for a three-dimensional hydrodynamic multi-species plasma model described by the Euler-Maxwell equations. Our method is inspired by and extends the one-dimensional scheme from $[$P.~Degond, F.~Deluzet, and D.~Savelief, \emph{Numerical approximation of the Euler-Maxwell model in the quasineutral limit}, Journal of Computational Physics, 231 (4), pp.~1917--1946, 2012$]$. It can cope with large variations of the Debye length $\lambda_D$ and is robust in the quasi-neutral limit $\lambda_D\to 0$ thanks to its \emph{asymptotic-preserving} (AP) property. The key ingredients of our approach are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of \emph{discrete exterior calculus} (DEC) also known as the finite integration technique (FIT), (ii) a finite volume method (FVM) for the fluid equations on the dual mesh, (iii) \emph{mixed implicit-explicit timestepping}, (iv) special no-flux and contact boundary conditions at an outer cut-off boundary, and (v) additional \emph{stabilization} in the non-conducting region outside the plasma domain based on direct enforcement of Gauss' law. Numerical tests provide strong evidence confirming the AP property of the proposed method.
